%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Tutor} % Job title
    {Cégep Garneau} % Organization
    {Quebec, QC} % Location
    {Jan. 2020 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Tutored in Physique Mécanique, Ondes et physique moderne, Calcul intégral and Chimie Générale.}
        \item {Gave in-person and remote tutoring to help students acquire greater knowledge and practice.}
        \item {Assisted in building and organizing student's schedules to perform better.}
        \item {Kept records of academic performance to address areas of improvement.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sales Representative} % Job title
    {Bravad Technologies (Remote)} % Organization
    {Montreal, QC} % Location
    {Sept. 2021 - Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Head of the used phones sales in the new remote department in Montreal.}
        \item {Creating appealing and descriptive listings of cellphones to sell.}
        \item {Developed and sustained relationships with existing clients.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Sales Representative} % Job title
    {Bravad Technologies (Telus/Koodo)} % Organization
    {Quebec, QC} % Location
    {June 2020 - Sept. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Recognized as a hardworking and performing employee.}
        \item {Participated in sales training events and conferences to continuously develop skills and gain product knowledge.}
        \item {Developed and sustained relationships with existing clients.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Lifeguard} % Job title
    {Ville de Québec} % Organization
    {Quebec, QC} % Location
    {June 2018 - Sept. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Served as lifeguard in busy pools. Provided rule enforcement, rescue, and customer service.}
        \item {Ensured pool rules were followed by adults and minors.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}
